Identifying regime transitions for water governance at a basin scale

### 2023-05-10 paper/diff/draft.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up''.
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019a,long2020,nickum2021}.
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019a}.

The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019a}.
Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.

>>>>

The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up''.
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.

The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019e}.
Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.

### 2023-05-10 paper/main/01_introduction.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being~\cite{gleeson2020a,gleeson2020b}.
As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water~\cite{ahlstrom2021,biermann2012,steffen2020}.
Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers~\cite{sivapalan2012,qin2014,abbott2019}.
Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance~\cite{best2019,dibaldassarre2019}.

>>>>

Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting development and human well-being~\cite{gleeson2020a,gleeson2020b}.
As an integral part of earth system governance, successful water governance requires a deep understanding of changes in the complex relationships between humans and water~\cite{ahlstrom2021,biermann2012,steffen2020}.
Human activities stemming from our reliance on water have profoundly modified the natural water cycle, resulting in rivers that are dominated by a hybrid of social and natural drivers~\cite{sivapalan2012,qin2014a,abbott2019}.
Facing transitions from natural to human-dominated regimes, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of more effective water governance~\cite{best2019,dibaldassarre2019}.

### 2023-05-10 paper/main/02_methods.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

	% 将三者合一起，即：
	As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three aspects (Stress, Purpose, and Allocation) of water governance. Each dimension keeps two directions, and we assumed the hydrosocial cycle aligns with one of them, respectively:
	\begin{equation}
		Transformation \propto S*P*A
	\end{equation}

@@

	\subsubsection*{Indicator of stress}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed in~\citeA{qin2019} to evaluate water stress.
	This metric considers management measures (such as the construction of reservoirs) and the impact of changes in water use structure on the evaluation of water scarcity.
	Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information S1}).
	For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
	\begin{equation}
		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
	\end{equation}

>>>>

	% 将三者合一起，即：
	As shown in the framework Figure~\ref{fig:framework}, the IWGI combines the three aspects (Stress, Purpose, and Allocation) of water governance:
	\begin{equation}
		Transformation \propto S*P*A
	\end{equation}

@@

	\subsubsection*{Indicator of stress}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed by \citeA{qin2019} to evaluate water stress.
	This indicator integrates the share of runoff being consumed, the share of consumption in these inflexible categories and the historical variability of runoff weighted by storage capacity~\cite{qin2019}, where impacts from both management measures and climate changes are included.
	% 这个指数得到了许多应用，是就我们已知范围内考虑因素最为齐全的，反应水资源压力的指数。
	The SFV-index, which has many applications, is the most comprehensive index of water stress we know. % todo citation

	Based on the hydrological and economic context of YRB, four second-level regions are divided (Source Region, Upper Region, Middle Region, and Lower Region, see \textit{Supporting Information S1}).
	For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
	\begin{equation}
		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
	\end{equation}

### 2023-05-10 paper/main/04_discussion.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming command (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
As the Chinese slogan ``man will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical~\cite{loch2020}.
Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016a}.

The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up''.
% 正如理论预测的那样
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
% 作为制度转变的先行者
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019a,long2020,nickum2021}.
% 因此，1999年黄河的最后一次枯竭
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019a}.

The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019a}.
Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.

% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012a}.
Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

>>>>

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming command (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
As the Chinese slogan ``man will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical~\cite{loch2020}.
Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.

The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up''.
% 正如理论预测的那样
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
% 作为制度转变的先行者
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
% 因此，1999年黄河的最后一次枯竭
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.

The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019e}.
Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.

% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
With each dimension changing gradually, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012}.
Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

Future's tightly intertwined socio-hydro interactions can lead water governance challenges even more complex and comprehensive, combining resources issues and structural barriers~\cite{huggins2022a}.
For example, climate change may alter water scarcity levels and make it more difficult to effectively use water due to extreme climate events, strengthening water stress and threatening infrastructures~\cite{liu2017, dibaldassarre2019}.
Additionally, adapting to climate change could lead to transformations~\cite{sachs2019,barnes2020}, prompting a reevaluation of governance strategies of social water usage (priority and allocation) which is being increasingly altered by current regime transitions.
It may be difficult to exhaust what is considered in a good watershed governance strategy, but the IWGI at least gives us a sense of where the a river basin is heading and how challenged.
